---
title: "Mess around with group lasso"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(hdrm)
library(glmnet)
library(grpreg)
library(dplyr)

set.seed(1)
```

# Simulation set up

- Sample size for both training and testing set is 200
- 50 covariates, 10 groups, 5 covariates each group
- group 1 and 3 are important, with beta = c(1, 2, 3, 4, 5)
- signal-to-noise ratio = 1
- use 10-fold CV to select lambda
- use prediction error to evaluate prediction
- did not use tuning parameter of weight, scaled them instead

# output from 1 iteration

```{r results='hide'}
source("../Code/toy_sim.R")
```

```{r}
data.frame("prediction error" = pred_error,
           "cost per prediction" = cpp,
           group = grp)

```

# output from 100 iterations

```{r results='hide'}
pe_list <- list()
cpp_list <- list()

# i <- 1
for(i in 1:1000){
  source("../Code/toy_sim.R")
  pe_list[[i]] <- pred_error
  cpp_list[[i]] <- cpp
}
```


```{r}
par(mfrow = c(1, 3))
cpp_df <- cpp_list %>% bind_rows()
boxplot(cpp_df$lasso, xlab = "Lasso") 
boxplot(cpp_df$`group lasso`, xlab = "Group lasso") 
boxplot(cpp_df$`group lasso with cost`, xlab = "Group lasso with cost") 
lapply(cpp_df, mean)
```

```{r}
par(mfrow = c(1, 3))
pe_df <- pe_list %>% bind_rows()
boxplot(pe_df$lasso, xlab = "Lasso") 
boxplot(pe_df$`group lasso`, xlab = "Group lasso") 
boxplot(pe_df$`group lasso with cost`, xlab = "Group lasso with cost") 
lapply(pe_df, mean)
```

# Questions

- still a lot of extreme values for prediction error
