---
title: "Simulation with model selection by BIC"
output:
  html_document:
    highlight: espresso
    number_sections: yes
    theme: yeti
    toc: yes
    toc_depth: 2
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(ncvreg)
library(grpreg)
library(hdrm)
library(dplyr)
library(reshape2)

set.seed(123)
```


# Simulation set up

- Sample size for both training and testing set is 200
- 50 covariates, 10 groups, 5 covariates each group
- group 1 and 3 are important, with beta = c(1, 2, 3, 4, 5)
- signal-to-noise ratio = 1
- use BIC to select lambda
- use prediction error to evaluate prediction
- tuning parameter of weight: 0, .25, .5, .75, 1, no scale. just used cost for weight
- cost randomly generated with each simulation
- solution path 

```{r}
load("../Data/sim_model_select.RData")
load("../Data/sim_model_once.RData")
```


# zero correlation for both inter and intra group

## Results

```{r, message=FALSE}
pe_df1 <- sim_pe1 %>% bind_rows() %>% melt()
cpp_df1 <- sim_cpp1 %>% bind_rows() %>% melt()
```


```{r, message=FALSE, fig.width=10}
par(mfrow = c(1,2))
boxplot(value ~ variable, data = pe_df1, ylab = "prediction error")
boxplot(value ~ variable, data = cpp_df1, ylab = "Cost per prediction")

pe_df1 %>% group_by(variable) %>% summarise(ave_pe = mean(value),
                                            med_pe = median(value)) 
cpp_df1 %>% group_by(variable) %>% summarise(ave_cpp = mean(value),
                                             med_cpp = median(value)) 
```

## Solution path

```{r, fig.height=7, fig.width=12}
par(mfrow = c(2, 2))
# lasso
plot(log(this_fit1$lasso$lambda), BIC(this_fit1$lasso), xlim = c(1, -10), main = "Lasso")
plot(this_fit1$lasso, log.l = T, xlim = c(1, -10))

# cost-ranked lasso
plot(log(this_fit1$crl$lambda), BIC(this_fit1$crl), xlim = c(1, -10), main = "CRL")
plot(this_fit1$crl, log.l = T, xlim = c(1, -10))
```


```{r, fig.height=7, fig.width=12}
par(mfrow = c(2, 2))
# group lasso
plot(log(this_fit1$gl$lambda), BIC(this_fit1$gl), xlim = c(1, -10), main = "GL")
plot(this_fit1$gl, log.l = T, xlim = c(1, -10))
# cost group lasso
plot(log(this_fit1$cgl$lambda), BIC(this_fit1$cgl), xlim = c(1, -10), main = "CGL")
plot(this_fit1$cgl, log.l = T, xlim = c(1, -10))
```


```{r, fig.height=7, fig.width=12}
# rCGL
par(mfrow = c(2, 2))
plot(log(this_fit1$rcgl[[1]]$lambda), BIC(this_fit1$rcgl[[1]]), xlim = c(1, -10), main = "rCGL (r = 0)")
plot(this_fit1$rcgl[[1]], log.l = T, xlim = c(1, -10))
# rcost group lasso, r = 0.25
plot(log(this_fit1$rcgl[[2]]$lambda), BIC(this_fit1$rcgl[[2]]), xlim = c(1, -10), main = "rCGL (r = 0.25)")
plot(this_fit1$rcgl[[2]], log.l = T, xlim = c(1, -10))
```

```{r, fig.height=7, fig.width=12}
par(mfrow = c(2, 2))
plot(log(this_fit1$rcgl[[3]]$lambda), BIC(this_fit1$rcgl[[3]]), xlim = c(1, -10), main = "rCGL (r = 0.5)")
plot(this_fit1$rcgl[[3]], log.l = T, xlim = c(1, -10))
plot(log(this_fit1$rcgl[[4]]$lambda), BIC(this_fit1$rcgl[[4]]), xlim = c(1, -10), main = "rCGL (r = 0.75)")
plot(this_fit1$rcgl[[4]], log.l = T, xlim = c(1, -10))
```

# zero between-group, 0.5 within group correlaion

## Results

```{r message=FALSE}
pe_df2 <- sim_pe2 %>% bind_rows() %>% melt()
cpp_df2 <- sim_cpp2 %>% bind_rows() %>% melt()
```


```{r message=FALSE, fig.width=10}
par(mfrow = c(1,2))
boxplot(value ~ variable, data = pe_df2, ylab = "prediction error")
boxplot(value ~ variable, data = cpp_df2, ylab = "Cost per prediction")
pe_df2 %>% group_by(variable) %>% summarise(ave_pe = mean(value),
                                            med_pe = median(value)) 
cpp_df2 %>% group_by(variable) %>% summarise(ave_cpp = mean(value),
                                             med_cpp = median(value)) 
```

## Solution path

```{r, fig.height=7, fig.width=12}
par(mfrow = c(2, 2))
# lasso
plot(log(this_fit2$lasso$lambda), BIC(this_fit2$lasso), xlim = c(1, -10), main = "Lasso")
plot(this_fit2$lasso, log.l = T, xlim = c(1, -10))
# ranked cost lasso
plot(log(this_fit2$crl$lambda), BIC(this_fit2$crl), xlim = c(1, -10), main = "CRL")
plot(this_fit2$crl, log.l = T, xlim = c(1, -10))
```

```{r, fig.height=7, fig.width=12}
par(mfrow = c(2, 2))
# group lasso
plot(log(this_fit2$gl$lambda), BIC(this_fit2$gl), xlim = c(1, -10), main = "GL")
plot(this_fit2$gl, log.l = T, xlim = c(1, -10))
# cost group lasso
plot(log(this_fit2$cgl$lambda), BIC(this_fit2$cgl), xlim = c(1, -10), main = "CGL (r = 1)")
plot(this_fit2$cgl, log.l = T, xlim = c(1, -10))
```

```{r, fig.height=7, fig.width=12}
# rCGL
par(mfrow = c(2, 2))
# rcost group lasso, r = 0.25
plot(log(this_fit2$rcgl[[1]]$lambda), BIC(this_fit2$rcgl[[1]]), xlim = c(1, -10), main = "rCGL (r = 0)")
plot(this_fit2$rcgl[[1]], log.l = T, xlim = c(1, -10))
# rcost group lasso, r = 0.25
plot(log(this_fit2$rcgl[[2]]$lambda), BIC(this_fit2$rcgl[[2]]), xlim = c(1, -10), main = "rCGL (r = 0.25)")
plot(this_fit2$rcgl[[2]], log.l = T, xlim = c(1, -10))
```

```{r, fig.height=7, fig.width=12}
par(mfrow = c(2, 2))
plot(log(this_fit2$rcgl[[3]]$lambda), BIC(this_fit2$rcgl[[3]]), xlim = c(1, -10), main = "rCGL (r = 0.5)")
plot(this_fit2$rcgl[[3]], log.l = T, xlim = c(1, -10))
plot(log(this_fit2$rcgl[[4]]$lambda), BIC(this_fit2$rcgl[[4]]), xlim = c(1, -8), main = "rCGL (r = 0.75)")
plot(this_fit2$rcgl[[4]], log.l = T, xlim = c(1, -10))
```

# 0.5 correlation for both between and within groups

## Results

```{r message=FALSE}
pe_df3 <- sim_pe3 %>% bind_rows() %>% melt()
cpp_df3 <- sim_cpp3 %>% bind_rows() %>% melt()
```


```{r message=FALSE, fig.width=10}
par(mfrow = c(1,2))
boxplot(value ~ variable, data = pe_df3, ylab = "prediction error")
boxplot(value ~ variable, data = cpp_df3, ylab = "Cost per prediction")
pe_df3 %>% group_by(variable) %>% summarise(ave_pe = mean(value),
                                            med_pe = median(value)) 
cpp_df3 %>% group_by(variable) %>% summarise(ave_cpp = mean(value),
                                             med_cpp = median(value)) 
```

## Solution path

```{r, fig.height=7, fig.width=12}
par(mfrow = c(2, 2))
# lasso
plot(log(this_fit3$lasso$lambda), BIC(this_fit3$lasso), xlim = c(1, -10), main = "Lasso")
plot(this_fit3$lasso, log.l = T, xlim = c(1, -10))
# cost ranked lasso
plot(log(this_fit3$crl$lambda), BIC(this_fit3$crl), xlim = c(1, -10), main = "CRL")
plot(this_fit3$crl, log.l = T, xlim = c(1, -10))
```

```{r, fig.height=7, fig.width=12}
par(mfrow = c(2, 2))
# group lasso
plot(log(this_fit3$gl$lambda), BIC(this_fit3$gl), xlim = c(1, -10), main = "GL")
plot(this_fit3$gl, log.l = T, xlim = c(1, -10))
# cost group lasso
plot(log(this_fit3$cgl$lambda), BIC(this_fit3$cgl), xlim = c(1, -10), main = "CGL (r = 1)")
plot(this_fit3$cgl, log.l = T)
```

```{r, fig.height=7, fig.width=12}
# rCGL
par(mfrow = c(2, 2))
# rcost group lasso, r = 0
plot(log(this_fit3$rcgl[[1]]$lambda), BIC(this_fit3$rcgl[[1]]), xlim = c(1, -10), main = "rCGL (r = 0)")
plot(this_fit3$rcgl[[1]], log.l = T, xlim = c(1, -10))
# rcost group lasso, r = 0.25
plot(log(this_fit3$rcgl[[2]]$lambda), BIC(this_fit3$rcgl[[2]]), xlim = c(1, -10), main = "rCGL (r = 0.25)")
plot(this_fit3$rcgl[[2]], log.l = T, xlim = c(1, -10))
```

```{r, fig.height=7, fig.width=12}
par(mfrow = c(2, 2))
plot(log(this_fit3$rcgl[[3]]$lambda), BIC(this_fit3$rcgl[[3]]), xlim = c(1, -8), main = "rCGL (r = 0.5)")
plot(this_fit3$rcgl[[3]], log.l = T)
plot(log(this_fit3$rcgl[[4]]$lambda), BIC(this_fit3$rcgl[[4]]), xlim = c(1, -8), main = "rCGL (r = 0.75)")
plot(this_fit3$rcgl[[4]], log.l = T)
```

